Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2021-08-02 paper/authorList.tex
adding commas

\author{Hannah Middleton}
\email{hannah.middleton@unimelb.edu.au}
\affiliation{%
School of Physics, University of Melbourne, Parkville, Victoria, 3010, Australia
}
\affiliation{%
Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia 
}
\affiliation{%
OzGrav-Melbourne, Australian Research Council Centre of Excellence for Gravitational Wave Discovery, Parkville, Victoria 3010, Australia
}

\author{Changrong Liu}
\affiliation{%
Department of Electrical and Electronic Engineering, University of Melbourne, Parkville, Victoria 3010, Australia
}
\affiliation{%
OzGrav-Melbourne, Australian Research Council Centre of Excellence for Gravitational Wave Discovery, Parkville, Victoria 3010, Australia
}

\author{Andrew Melatos}
\email{amelatos@unimelb.edu.au}
\affiliation{%
School of Physics, University of Melbourne, Parkville, Victoria, 3010, Australia
}
\affiliation{%
OzGrav-Melbourne, Australian Research Council Centre of Excellence for Gravitational Wave Discovery, Parkville, Victoria 3010, Australia
}

\author{Robin Evans}
\affiliation{%
Department of Electrical and Electronic Engineering, University of Melbourne, Parkville, Victoria 3010, Australia
}
\affiliation{%
OzGrav-Melbourne, Australian Research Council Centre of Excellence for Gravitational Wave Discovery, Parkville, Victoria 3010, Australia
}

\author{William Moran}
\affiliation{%
Department of Electrical and Electronic Engineering, University of Melbourne, Parkville, Victoria 3010, Australia
}

>>>>

\author{Hannah Middleton}
\email{hannah.middleton@unimelb.edu.au}
\affiliation{%
School of Physics, University of Melbourne, Parkville, Victoria, 3010, Australia
}
\affiliation{%
Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria, 3122, Australia 
}
\affiliation{%
OzGrav-Melbourne, Australian Research Council Centre of Excellence for Gravitational Wave Discovery, Parkville, Victoria, 3010, Australia
}

\author{Changrong Liu}
\affiliation{%
Department of Electrical and Electronic Engineering, University of Melbourne, Parkville, Victoria, 3010, Australia
}
\affiliation{%
OzGrav-Melbourne, Australian Research Council Centre of Excellence for Gravitational Wave Discovery, Parkville, Victoria, 3010, Australia
}

\author{Andrew Melatos}
\email{amelatos@unimelb.edu.au}
\affiliation{%
School of Physics, University of Melbourne, Parkville, Victoria, 3010, Australia
}
\affiliation{%
OzGrav-Melbourne, Australian Research Council Centre of Excellence for Gravitational Wave Discovery, Parkville, Victoria, 3010, Australia
}

\author{Robin Evans}
\affiliation{%
Department of Electrical and Electronic Engineering, University of Melbourne, Parkville, Victoria, 3010, Australia
}
\affiliation{%
OzGrav-Melbourne, Australian Research Council Centre of Excellence for Gravitational Wave Discovery, Parkville, Victoria, 3010, Australia
}

\author{William Moran}
\affiliation{%
Department of Electrical and Electronic Engineering, University of Melbourne, Parkville, Victoria, 3010, Australia
}
